FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-07-19 paper.tex
ganesh orcid, start rel work
more rw notes

>>>>

Error analysis, typical answer.
Difficult.
CITE

Toronto McCarthy lightweight plotting approach.
No tool support.

Herbie, improving accuracy automatically.
ParetoHerbie

%% http://eprints.maths.manchester.ac.uk/2873/1/fami22.pdf
%% https://drive.google.com/drive/folders/1HkgMpxi6hsqLSZj9tSnuCxnFExPPjmvx?usp=sharing
%% https://docs.google.com/presentation/d/1ueqzb5QY9YHmtY2DfY_hpN9oufSOcXErLWsJOZQxgzo/edit?usp=sharing
%% https://ieeexplore.ieee.org/document/8916392
%% https://link.springer.com/chapter/10.1007/978-3-319-73721-8_24

%% Demmel, somewhere!
%% https://arxiv.org/pdf/2207.09281.pdf

Sherlogs, ShallowWaters
%% https://github.com/milankl/Sherlogs.jl
%% sherlogs

FPSpy x86 binaries [10]
Dinda etal hpdc 2020

FPChecker, " considers CPU OpenMP and MPI codes, again using LLVM
instrumentation"~\cite{ltlg-iiswc-2022}

6-8,24,25
Arnab Das scalable yet rigorous
Marc Daumas Certification of Bounds Expres
David Delmas Towards an Industrial Use of
Alexey Solovyev FPTaylor Results table
Titolo absint

CSTG~\cite{hmbdrg-cse-2014}.
What else???

GPU-FPX state of art, companion project~\cite{llsflg-hpdc-2023}.
Latest in line of work.
BinFPE exn checking, slower than GPU-FPX, 
\cite{llg-soap-2022}.
FPChecker, early pioneer, fpx in gpus, llvm-level instrumentation
if compiled with Clang, but most gpus use closed NVCC compiler~\cite{l-ase-2019}.
